---
title: "icbc"
author: "Lincy Antony"
date: "29/12/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r }
library(tidyverse)

library(recipes)
library(visdat)

library(stats)
library(ggplot2)
library(dplyr)
library(plyr)

B_COL<-read.csv("C:/Users/lincy/OneDrive/Desktop/icbc/British_Columbia.csv")
head(B_COL,10)
View(B_COL)
```


```{r}
sum(is.na(B_COL))

vis_dat(B_COL,warn_large_data= FALSE)

glimpse(B_COL)

B_COL <- B_COL[complete.cases(B_COL), ]

```

```{r}

Clean_data <- B_COL %>%
 recipe(~., data= B_COL) %>%
  step_select(-Latitude, -Longitude,-Street.Full.Name..ifnull.,-Road.Location.Description, -Cross.Street.Full.Name) %>%
 step_mutate(
 Crash.Severity = factor(case_when(
 Crash.Severity == "CASUALTY CRASH" ~ 0,
 Crash.Severity == "PROPERTY DAMAGE ONLY" ~ 1)
), 
  Derived.Crash.Configuration = factor(Derived.Crash.Configuration, levels=c( "", "CONFLICTED","HEAD ON", "MULTIPLE IMPACTS","OVERTAKING","REAR END", "REAR TO REAR","SIDE IMPACT" ,"SIDE SWIPE - SAME DIRECTION","SIDE SWIPE -OPPOSITE DIRECTION", "SINGLE VEHICLE", "UNDETERMINED" ),
  labels =c(0,1,2,3,4,5,6,7,8,9,10,11)), 
  Day.Of.Week = factor(Day.Of.Week, levels=c("SUNDAY", "MONDAY","TUESDAY","WEDNESDAY","THURSDAY","FRIDAY" ,"SATURDAY"),labels=c(1,2,3,4,5,6,7)),
Intersection.Crash = factor(case_when(
 Intersection.Crash == "" ~ 0,
 Intersection.Crash == "No" ~ 0,
 Intersection.Crash== "Yes" ~ 1)),
Parking.Lot.Flag = factor(case_when(
 Parking.Lot.Flag == "" ~ 0,
 Parking.Lot.Flag == "No" ~ 0,
 Parking.Lot.Flag== "Yes" ~ 1)),
 Pedestrian.Flag = factor(case_when(
 Pedestrian.Flag == "" ~ 0,
 Pedestrian.Flag == "No" ~ 0,
 Pedestrian.Flag == "Yes" ~ 1)),
Month.Of.Year = factor(Month.Of.Year, levels=c("JANUARY","FEBRUARY","MARCH","APRIL" ,"MAY","JUNE","JULY","AUGUST","SEPTEMBER","OCTOBER","NOVEMBER","DECEMBER"),labels=c(1,2,3,4,5,6,7,8,9,10,11,12)))%>%step_nzv(all_predictors())  %>% prep(B_COL) %>% bake(B_COL) 




view(Clean_data)

```


Exploratory data:


```{R}

Clean_data %>% 
select(c("Day.Of.Week","Total.Victims"))%>%group_by(Day.Of.Week)%>%dplyr::summarize(Total_Victims=sum(Total.Victims)) 


```


```{R}

Clean_data %>% 
select(c("Month.Of.Year","Total.Victims"))%>%group_by(Month.Of.Year)%>%dplyr::summarize(Total_Sales=sum(Total.Victims))


```

November and december are having more crashes.

```{R}

Clean_data %>% 
select(c("Day.Of.Week","Crash.Severity"))%>%group_by(Crash.Severity)%>%tally()


```

```{R}

#Clean_data %>% select(c("Day.Of.Week","Crash.Severity"))%>%group_by(Day.Of.Week)%>%summarize(cou=n(),groups = 'drop') 

aggregate(B_COL$Day.Of.Week, by=list(B_COL$Crash.Severity,B_COL$Day.Of.Week), FUN=length)

#Clean_data %>%select(c("Pedestrian.Flag","Parking.Lot.Flag","Intersection.Crash"))%>% group_by(Pedestrian.Flag, Parking.Lot.Flag, Intersection.Crash) %>% summarise(n=n()) #%>%ungroup() %>% group_by(n) %>% summarise(total=n())


```



Derived cash configuration vs year vs crash severity


```{r}
Clean_data %>% ggplot(aes(x=Derived.Crash.Configuration, fill=Crash.Severity)) + geom_bar(position="dodge")

```


```{r}
Clean_data %>% ggplot(aes(x=Intersection.Crash, fill=Crash.Severity)) + geom_bar(position="dodge")


```

Data cleaning:


Exploratory data:






Crash severity ratio over the years:

which day of the week is having more crashes by region:

time during the crash

Trend of the crashes over the years:

What kind of impact is causing more severity.




focus on vancouver - clustering 


